Visual narratives of the Covid-19 pandemic

### 2022-01-24 JDSSV_manuscript_submitted.Rnw
blinded manuscript included

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Susan Vanderplas\\University of Nebraska–Lincoln
   \And Adalbert F.X. Wilhelm\\Jacobs University Bremen}
\Plainauthor{Susan Vanderplas, Adalbert F.X. Wilhelm}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
    email: \email{susan.vanderplas@unl.edu}
  Susan Vanderplas\\
  Department of Statistics\\
  University of Nebraska–Lincoln\\
  349A Hardin Hall \\
  Lincoln, NE 68583-0963, USA\\
  E-mail: \email{susan.vanderplas@unl.edu}\\
  URL: \url{https://statistics.unl.edu/susan-vanderplas}\\
\ \\
%}
%
%\Address{
  Adalbert F.X. Wilhelm\\
  Department of Psychology and Methods\\
  Jacobs University Bremen gGmbH\\
  Campus Ring 1\\
  28759 Bremen, Germany\\
  E-mail: \email{a.wilhelm@jacobs-university.de}\\
  URL: \url{http://www.jacobs-university.de/directory/wilhelm}
}

>>>>

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{
   \And }
\Plainauthor{}

@@

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
}
